Reasoning About a Machine with Local Capabilities

### 2019-08-24 toplas/paper.tex
Some tuning for the TOPLAS camera-ready submission.
Add another phrase to acks.

\documentclass[format=acmsmall, review=true, screen=true]{acmart}

@@

\author{Dominique~Devriese}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
%  \position{Position1}
  \department{Vakgroep Computerwetenschappen}              %% \department is recommended
  \institution{Vrije Universiteit Brussel}            %% \institution is required
  \streetaddress{Pleinlaan 2}
  \city{Elsene}
  \postcode{1050}
  \country{Belgium}
}
\email{dominique.devriese@vub.be}          %% \email is recommended

@@

@@

\begin{acks}
This research was supported in part by the ModuRes Sapere Aude Advanced Grant
from The Danish Council for Independent Research for the Natural Sciences (FNU). 
Support for an STSM was received from COST Action EUTypes (CA15123).
Dominique Devriese holds a Postdoctoral fellowship from the Research Foundation Flanders (FWO).
\end{acks}

%% Acknowledgments
% \begin{acks}                            %% acks environment is optional
%                                         %% contents suppressed with 'anonymous'
%   %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
%   %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
%   %% acknowledge financial support and will be used by metadata
%   %% extraction tools.
%   This material is based upon work supported by the
%   \grantsponsor{GS100000001}{National Science
%     Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
%   No.~\grantnum{GS100000001}{nnnnnnn} and Grant
%   No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
%   conclusions or recommendations expressed in this material are those
%   of the author and do not necessarily reflect the views of the
%   National Science Foundation.
% \end{acks}

>>>>

\documentclass[format=acmsmall, screen=true]{acmart}

@@

\author{Dominique~Devriese}
\orcid{0000-0002-3862-6856}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
%  \position{Position1}
  \department{Vakgroep Computerwetenschappen}              %% \department is recommended
  \institution{Vrije Universiteit Brussel}            %% \institution is required
  \streetaddress{Pleinlaan 2}
  \city{Elsene}
  \postcode{1050}
  \country{Belgium}
}
\email{dominique.devriese@vub.be}          %% \email is recommended

@@

\keywords{capability machines, CHERI, local capabilities, well-bracketed control
flow, stack encapsulation, logical relations, secure compilation}

@@

\begin{acks}
This research was supported in part by the ModuRes Sapere Aude Advanced Grant
from The Danish Council for Independent Research for the Natural Sciences (FNU). 
Support for an STSM was received from COST Action EUTypes (CA15123).
Dominique Devriese held a Postdoctoral fellowship from the Research Foundation
Flanders (FWO) during most of this research.
This research was supported in part by the Research Foundation Flanders (FWO).
\end{acks}
